% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref,url}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[sc,osf]{mathpazo}
%\usepackage{tgtermes}

% Set your name here
\def\name{Patricio Jeraldo}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://guava.physics.uiuc.edu/~patricio/CV.html}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {microbiome,metagenomics,microbial genomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.45\linewidth}
\vspace{0pt}
  \href{http://mayoclinic.org}{Mayo Clinic} \\
  200 First Street SW \\
  Rochester, MN 55905
\end{minipage}
\begin{minipage}[t]{0.45\linewidth}
\vspace{0pt}
  \begin{tabular}{ll}
    Phone: & +1 (507) 284-2229 \\
    %Fax: &  (919) 962-5678 \\
    Email: & \href{mailto:jeraldo.patricio@mayo.edu}{\tt jeraldo.patricio@mayo.edu} \\
%    Homepage: & \href{http://guava.physics.uiuc.edu/~patricio}{\url{
%    http://guava.physics.uiuc.edu/~patricio}}
    \\
  \end{tabular}
\end{minipage}


\section*{Personal}

\begin{itemize}
\item Citizenship: Chilean Citizen
\item US Visa status / work authorization: H-1B (Sponsor: Mayo Clinic)
%\item Languages: Spanish: native; English: read, written and spoken (TOEFL: 640 PBT, TWE: 5, SPEAK: 50)
\item Languages: Spanish: native; English: read, written and spoken
\end{itemize}

\section*{Academic and Research Interests}

\begin{itemize}
  \item Quantitative and Computational Biology, Microbial Ecology and
Metagenomics, Microbial Systems Biology, Bioinformatics
\end{itemize}

\section*{Employment}
\subsection*{Professional appointments}
\begin{itemize}
\item March 2015 -- Current: Research Scientist, Department of Surgery, Mayo Clinic
\end{itemize}
\subsection*{Postdoctoral}
\begin{itemize}
\item April 2012 -- March 2015: Carl R. Woese Institute for Genomic Biology, University of Illinois at Urbana-Champaign
\item April 2012 -- March 2015: Department of Surgery, Mayo Clinic (joint with U. of Illinois)
\end{itemize}
%\subsection*{Teaching - University of Illinois at Urbana-Champaign}
%\begin{itemize}
%\item Thermal and Statistical Physics (University), Fall II 2011, Teaching Assistant (Discussion) %for Raffi Budakian
%\item Quantum Physics (University), Fall I 2011, Teaching Assistant (Discussion) %for Raffi Bhudakian
%\item Electricity \& Magnetism and Modern Physics (College), Spring 2010,
%Teaching Assistant (Discussion) %for Yann Chemla
%\item Mechanics and Heat (College), Fall 2008, Teaching Assistant (Lab)
% for Charles Gammie
%\item Electricity \& Magnetism and Modern Physics (College), Spring 2007,
%Teaching Assistant (Lab) % for George Gollin
%\item Electricity \& Magnetism and Modern Physics (College), Fall 2006,
%Teaching Assistant (Lab) % for George Gollin
%\item Atomic and Quantum Physics (Phys. Major), Spring 2005,
%Teaching Assistant (Grading) % for DVH
%\item Atomic and Quantum Physics (Phys. Major), Fall
%2004, Teaching Assistant (Grading) % for DVH
%\end{itemize}
%\subsection*{Teaching - Universidad de Chile}
%\begin{itemize}
%  \item Contemporary Physics (Engr. Major), Fall 2003, Teaching Assistant
%  (Discussion) % Rene Mendez
%  \item Computational Methods in Physics (Phys. Major), Spring 2002, Teaching
%  Assistant % Patricio Cordero
%  \item Electromagnetism (Engr. Major), Fall 2002, Teaching Assistant
%  (Discussion) % Patricio Cordero
%  \item Introductory Modern Physics (Phys. Major), Spring 2001, Teaching
%  Assistant (Discussion) % Nelson Zamorano
%  \item Contemporary Physics (Engr. Major), Fall 2001, Teaching Assistant
%  (Discussion) % Daphne Boys
%\end{itemize}
%\subsection*{Other}
%\begin{itemize}
%  \item Physics Computer Services - Dept. of Physics, Univ. of Illinois at
%  Urbana Champaign, Summer 2005 - Spring 2006, Graduate Assistant (Tech Support)
%\end{itemize}

\section*{Education}

\begin{itemize}
  \item Ph.D. Physics, University of Illinois at Urbana-Champaign, 2012 \\
  Thesis: Computational approaches to stochastic systems in physics and ecology \\
  Advisor: Nigel Goldenfeld

  \item M.S. Physics, University of Illinois at Urbana-Champaign, 2007

  \item Magíster en Ciencias mención Física (equivalent to M.Sc. Physics),
  Universidad de Chile, 2004\\ Thesis: Quantitative Model for the Growth of Biomaterials: A Study of Avian
  Eggshell \\
  Advisor: Fernando Lund

  \item Licenciatura en Ciencias mención Física (equivalent to B.Sc. Physics),
  Universidad de Chile, 2002
\end{itemize}

\section*{Skills}
\begin{itemize}
    \item Scripting in Python, Bash and R, with emphasis on numerical and bioinformatics modules
    \item Numerical programming in C/C++, Matlab, Java
%    \item User level knowledge of parallel computing queuing systems (SGE/OGE)
%    \item Basic knowledge of parallel computing libraries (MPI) and general purpose GPU computing
    \item Construction bioinformatics pipelines for high-throughput
    data analysis for 16S rRNA, shotgun metagenomics and clinical-grade microbial genome assembly
%    \item Proficiency in administering Linux/UNIX systems
\end{itemize}


\section*{Awards and Honors}
\begin{itemize}
  \item L.S. Edelheit Family Biological Physics Fellowship, 2009
  \item Teacher Ranked as Excellent, Physics 102 - College Physics: Electricity
  \& Magnetism and Modern Physics, Spring 2006
  \item Teacher Ranked as Outstanding, Physics 102 - College Physics: Electricity
  \& Magnetism and Modern Physics, Spring 2007
  \item Teacher Ranked as Excellent, Physics 101 - College Physics: Mechanics
  and Heat, Fall 2008
  \item Teacher Ranked as Outstanding, Physics 213/214 - University Physics: Thermal
  and Statistical Physics, Quantum Physics, Fall 2011
  \item Phi Kappa Phi Honor Society
\end{itemize}

\section*{Publications}

\begin{itemize}
\item \textbf{P. Jeraldo}, J.L. Arias, F. Lund, S. Maeckelberghe and D.
Walgraef, \textit{Towards a quantitative model of eggshell growth: a
two-dimensional study}, in Proceedings of the 9th International Symposium on Biomineralization,
edited by J.L. Arias and M.S. Fernández (Editorial Universitaria, Santiago,
Chile, 2007), pp. 155-164
\item M. Sipos, \textbf{P. Jeraldo}, N. Chia, A. Qu, A.S. Dhillon, M.E. Konkel,
K.E. Nelson, B. White, and N. Goldenfeld,
\textit{Robust Computational Analysis of rRNA Hypervariable Tag Datasets},
PLOS ONE \textbf{5},
\href{http://www.plosone.org/article/info:doi/10.1371/journal.pone.0015220}{e15220} (2010)
\item \textbf{P. Jeraldo}, N. Chia, and N. Goldenfeld, \textit{On the
Suitability of Short Reads of 16S rRNA for Phylogeny-based Analyses in Environmental Surveys},
Environ. Microbiol. \textbf{13},
\href{http://doi.wiley.com/10.1111/j.1462-2920.2011.02577.x}{3000-3009} (2011)

\item J. Brulc, C. Yeoman, M. Wilson, M. Berg-Miller, \textbf{P. Jeraldo},
S. Jindou, N. Goldenfeld, H. Flint, R. Lamed, M. Vodovnik, I. Borovok, K. E. Nelson,
E. Bayer, and B. White, \textit{Cellulosomics, a Gene-Centric Approach to
Investigating the Intraspecific Diversity and Adaptation of Ruminococcus
flavefaciens within the Rumen}, PLOS ONE \textbf{6},
\href{http://www.plosone.org/article/info:doi/10.1371/journal.pone.0025329}{
e25329} (2011)
\item L. Angheluta, \textbf{P. Jeraldo}, and N. Goldenfeld, \textit{Anisotropic
velocity statistics of topological defects under shear flow}, Phys. Rev. E
\textbf{85}, \href{http://link.aps.org/doi/10.1103/PhysRevE.85.011153}{011153}
(2012) (also at \href{http://arxiv.org/abs/1201.5758}{arXiv:1201.5758})
%\item L. Angheluta, \textbf{P. Jeraldo}, K. Dahmen and N. Goldenfeld,  \textit{Avalanche
%statistics and intermittency in topological defect-dominated flows}, submitted,
%\href{http://arxiv.org/abs/1103.2185}{arXiv:1103.2185}
\item \textbf{P. Jeraldo}, M. Sipos, N. Chia, J.M. Brulc, A.S. Dhillon, M.E. Konkel, C.L. Larson,
K.E. Nelson, A. Qu, L.B. Schook, F. Yang, B.A. White and N. Goldenfeld,
\textit{Quantification of the relative roles of niche and neutral processes in structuring gastrointestinal microbiomes},
Proc. Nat. Acad. Sci. USA \textbf{109}, \href{http://dx.doi.org/10.1073/pnas.1206721109}{9692-9698} (2012)
\item C. Yeoman, N. Chia, \textbf{P. Jeraldo}, M. Sipos, N. Goldenfeld and B.A. White,
\textit{The microbiome of the chicken gastroinstestinal tract},
Anim. Health Res. Rev. \textbf{13}, \href{http://dx.doi.org/10.1017/S1466252312000138}{89-99} (2012)
\item M.R.S. Walther-António, \textbf{P. Jeraldo}, M. Berg-Miller, C.J. Yeoman, K.E. Nelson, B.A. Wilson, B.A. White, N. Chia and D.J. Creedon, \textit{Pregnancy's Stronghold on the Vaginal Microbiome}, PLoS ONE \textbf{9}, \href{http://dx.plos.org/10.1371/journal.pone.0098514.g008}{e98514} (2014)
\item S.S Kang, \textbf{P.R. Jeraldo}, A. Kurti1, M.E. Berg-Miller, M. D. Cook, K. Whitlock, N. Goldenfeld, J.A. Woods, B.A. White, N. Chia and J.D. Fryer, \textit{Diet and exercise orthogonally alter the gut microbiome and reveal independent associations with anxiety and cognition}, Mol. Neurodegener. \textbf{9},  \href{http://dx.doi.org/10.1186/1750-1326-9-36}{6} (2014)
\item A.G. Theofiles, S.A. Cunningham, N. Chia, \textbf{P. Jeraldo}, D.J. Quest, J.N. Mandrekar and R. Patel, \textit{Pertussis Outbreak, Southeastern Minnesota, 2012}, Mayo Clin. Proc. \textbf{89}, \href{http://dx.doi.org/10.1016/j.mayocp.2014.08.004}{1378-1388} (2014)
\item C.T. Seto, \textbf{P. Jeraldo}, R. Orenstein, N. Chia and J.K. DiBaise,
\textit{Prolonged use of a proton pump inhibitor reduces microbial diversity: implications for Clostridium difficile susceptibility}, Microbiome \textbf{2}, \href{http://dx.doi.org/10.1186/2049-2618-2-42}{42} (2014)
\item \textbf{P. Jeraldo}, K. Kalari, X. Chen, J. Bhavsar, A. Mangalam, B.A. White, H. Nelson, J-P. Kocher and N. Chia, \textit{IM-TORNADO: A Tool for Comparison of 16S Reads from Paired-End Libraries}, PLOS ONE \textbf{9}, \href{http://dx.plos.org/10.1371/journal.pone.0114804}{e114804}
\item A.G. Braundmeier, K.M. Lenz, K.S. Inman, N. Chia, \textbf{P. Jeraldo}, M.R.S. Walther-António, M.E. Berg-Miller, F. Yang, D.J. Creedon, H. Nelson and B.A. White,
\textit{Individualized medicine and the microbiome in reproductive tract}, Front. Physiol. \textbf{6},
\href{http://dx.doi.org/10.3389/fphys.2015.00097}{97} (2015)
\item S.P. Sadarangani, S.A. Cunningham, \textbf{P.R. Jeraldo}, J.W. Wilson, R. Khare and R. Patel,
\textit{Metronidazole- and carbapenem-resistant Bacteroides thetaiotaomicron, Rochester, Minnesota 2014},
Antimicrob. Agents Che\-mo\-ther. \textbf{59}, \href{http://dx.doi.org/10.1128/AAC.00677-15}{4157--4161} (2015)
\item \textbf{P.R. Jeraldo}, Á. Hernández, B.A. White, D. O’Brien, D. Ahlquist, L. Boardman and N. Chia,
\textit{Draft Genome Sequences of 24 Microbial Strains Assembled from Direct Sequencing from 4 Stool Samples},
Genome Announc. \textbf{3}, \href{http://dx.doi.org/10.1128/genomeA.00526-15}{e00526--15}
\item \textbf{P.R. Jeraldo}, S.A. Cunningham, D. Quest, R.A. Sikkink, D. O’Brien, B.W. Eckloff, R. Patel, N. Chia,
\textit{Draft Genome Sequences of Nine Pseudomonas aeruginosa Strains, Including Eight Clinical Isolates},
Genome Announc. \textbf{3}, \href{http://dx.doi.org/10.1128/genomeA.01154-15}{e01154--15}
\item A.P. Norgan, J.M. Freese, P.M. Tuin, S.A. Cunningham, \textbf{P.R. Jeraldo} and R. Patel,
\textit{Carbapenem- and Colistin-Resistant Enterobacter cloacae, Delta, Colorado, 2015},
Antimicrob. Agents Chemother. \textbf{60}, \href{http://dx.doi.org/10.1128/AAC.03055-15}{3141--3144} (2016)
\item M.E. Hasassri, T.G. Boyce, A. Norgan, S.A. Cunningham, \textbf{P.R. Jeraldo}, S. Weissman, R. Patel, R. Banerjee, J.M. Pogue and K.S. Kaye,
\textit{An Immunocompromised Child with Bloodstream Infection Caused by Two Escherichia coli Strains, One Harboring NDM-5 and the Other Harboring OXA-48-Like Carbapenemase},
Antimicrob. Agents Chemother. \textbf{60}, \href{http://dx.doi.org/10.1128/AAC.03118-15}{3270--3275} (2016)
\item J. Chen, K. Wright, J.M. Davis, \textbf{P.R. Jeraldo}, E.V. Marietta, J. Murray, H. Nelson, E.L. Matteson and V. Taneja,
\textit{An expansion of rare lineage intestinal microbes characterizes rheumatoid arthritis},
Genome Med. \textbf{8}, \href{http://dx.doi.org/10.1186/s13073-016-0299-7}{43} (2016)
\item \textbf{P. Jeraldo}, Á. Hernández, H.B. Nielsen, X. Chen, B.A. White, N. Goldenfeld, H. Nelson, L. Boardman, D. Ahlquist and N. Chia,
\textit{Capturing one of the human gut microbiome’s most wanted: reconstructing the genome of a novel butyrate-producing, clostridial scavenger from metagenomic sequence data},
Front. Microbiol. \textbf{7}, \href{http://dx.doi.org/10.3389/fmicb.2016.00783}{783} (2016)
\item M. Thoendel, \textbf{P.R. Jeraldo}, K.E Greenwood-Quaintance, J.Z. Yao, N. Chia, A.D. Hanssen, M.P. Abdel, and R. Patel,
\textit{Comparison of microbial DNA enrichment tools for metagenomic whole genome sequencing},
J. Microbiol. Methods \textbf{127}, \href{http://dx.doi.org/10.1016/j.mimet.2016.05.022}{141--145} (2016)
\item E.V. Marietta, J.A. Murray, D.H. Luckey, \textbf{P.R. Jeraldo}, A. Lamba, R. Patel, H.S. Luthra, A. Mangalam and V. Taneja,
\textit{Human Gut-Derived Prevotella histicola Suppresses Inflammatory Arthritis in Humanized Mice},
Arthritis Rheumatol. \textbf{68}, \href{http://dx.doi.org/10.1002/art.39785}{2878--2888} (2016)
\item J. Chen, N. Chia, K.R. Kalari, J.Z. Yao, M. Novotna, M.M.P. Soldan, D.H. Luckey, E.V. Marietta, \textbf{P.R. Jeraldo}, X. Chen, B.G. Weinshenker, M. Rodriguez, O.H. Kantarci, H. Nelson, J.A. Murray and A.K. Mangalam,
\textit{Multiple sclerosis patients have a distinct gut microbiota compared to healthy controls},
Sci. Rep. \textbf{6}, \href{http://dx.doi.org/10.1038/srep28484}{28484} (2016)

\end{itemize}

%\section*{Presentations}
%\subsection*{Talks}
%\begin{itemize}
%  \item \textit{Evolutionary dynamics of a rare biosphere in the chicken
%  caecum}, Biocomplexity Theme Seminar, Institute for Genomic Biology,
%  Univeristy of Illinois at Urbana-Champaign, March 2009
%  \item \textit{Quantitative Model for the Growth of Biomaterials},
%  2nd SBPMat Meeting, Rio de Janeiro, Brazil, October 2003
%\end{itemize}

%\subsection*{Posters}
%\begin{itemize}
%  \item \textit{Deep metagenomic sequencing for de novo assemblies of genomes from the gut microbiota},
%  Keystone Symposia: Exploiting and Understanding Biochemical Transformations in the Human Microbiome,
%  Big Sky, MT, April 2014
%  \item \textit{De novo hybrid sequence assembly of metagenomes from human gut communities},
%  Cell Symposia: Microbiome and Host Health, Lisbon, Portugal, May 2013
%  \item \textit{TORNADO v2: a pipeline for alignments and comparison for
%  microbiome read libraries from next-generation sequencing platforms},
%  Individualizing Medicine Conference 2012, Mayo Clinic, Rochester, MN,
%  October 2012
%  \item \textit{On the suitability of short reads of 16S rRNA for
%  phylogeny-based analyses in environmental surveys}, Keystone Symposia:
%  Microbial Communities as Drivers of Ecosystem Complexity, Breckenridge, CO,
%  March 2011
%  \item \textit{Collective Dynamics of HGT}, Institute for Genomic Biology
%  Fellows Symposium, University of Illinois at Urbana-Champaign, February 2007
%  \item \textit{Quantitative Model for the Growth of Biomaterials}, 10th
%  International Workshop on Instabilities and Non\-equilibrium Structures, Viña
%  del Mar, Chile, December 2003
%\end{itemize}

\section*{References}
\begin{itemize}
  \item Prof. Nicholas Chia, email:
  \href{mailto:chia.nicholas@mayo.edu}{\texttt{chia.nicholas@mayo.edu}}
  \item Prof. Nigel Goldenfeld, email:
  \href{mailto:nigel@uiuc.edu}{\texttt {nigel@uiuc.edu}}
  \item Prof. Bryan White, email:
  \href{mailto:bwhite44@illinois.edu}{\texttt{bwhite44@illinois.edu}}
\end{itemize}
 \bigskip

 % Footer
 \begin{center}
   \begin{footnotesize}
     Last updated: \today \\
     %\href{\footerlink}{\url{\footerlink}}
   \end{footnotesize}
 \end{center}

\end{document}
